\documentclass[]{elsarticle} %review=doublespace preprint=single 5p=2 column
%%% Begin My package additions %%%%%%%%%%%%%%%%%%%
\usepackage[hyphens]{url}

  \journal{Journal of Transport Geography} % Sets Journal name


\usepackage{lineno} % add

\usepackage{graphicx}
%%%%%%%%%%%%%%%% end my additions to header

\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \usepackage{fontspec}
  \ifxetex
    \usepackage{xltxtra,xunicode}
  \fi
  \defaultfontfeatures{Mapping=tex-text,Scale=MatchLowercase}
  \newcommand{\euro}{€}
\fi
% use microtype if available
\IfFileExists{microtype.sty}{\usepackage{microtype}}{}
\bibliographystyle{elsarticle-harv}
\ifxetex
  \usepackage[setpagesize=false, % page size defined by xetex
              unicode=false, % unicode breaks when used with xetex
              xetex]{hyperref}
\else
  \usepackage[unicode=true]{hyperref}
\fi
\hypersetup{breaklinks=true,
            bookmarks=true,
            pdfauthor={},
            pdftitle={Introducing spatial availability, a singly-constrained competitive-access accessibility measure},
            colorlinks=false,
            urlcolor=blue,
            linkcolor=magenta,
            pdfborder={0 0 0}}
\urlstyle{same}  % don't use monospace font for urls

\setcounter{secnumdepth}{0}
% Pandoc toggle for numbering sections (defaults to be off)
\setcounter{secnumdepth}{0}


% tightlist command for lists without linebreak
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}






\begin{document}


\begin{frontmatter}

  \title{Introducing spatial availability, a singly-constrained
competitive-access accessibility measure}
    \author[SEES]{Anastasia Soukhov\corref{1}}
   \ead{soukhoa@mcmaster.ca} 
    \author[SEES]{Antonio Paez}
   \ead{paezha@mcmaster.ca} 
    \author[UofTS]{Christopher D. Higgins}
   \ead{cd.higgins@utoronto.ca} 
    \author[CIVENG]{Moataz Mohamed}
   \ead{mmohame@mcmaster.ca} 
      \address[SEES]{School of Earth, Environment and Society, McMaster
University, Hamilton, ON, L8S 4K1, Canada}
    \address[UofTS]{Department of Geography \& Planning, University of
Toronto Scarborough, 1265 Military Trail, Toronto, ON M1C1A4}
    \address[CIVENG]{Department of Civil Engineering, McMaster
University, Hamilton, ON, L8S 4K1, Canada}
      \cortext[1]{Corresponding Author}
  
  \begin{abstract}
  Accessibility measures are widely used in transportation, urban and
  healthcare planning, among other applications. These measures are
  weighted sums of the opportunities that can be reached given the cost
  of movement and are interpreted to represent the potential for spatial
  interaction. Though these measures are useful in understanding spatial
  structure, their methodologies count available opportunities multiple
  times. This leads to interpretability issues, as noted in recent
  research on balanced floating catchment areas (BFCA) and competitive
  measures of accessibility. In this paper, we respond to the
  limitations of the accessibility measure by proposing a new measure of
  \emph{spatial availability} which is calculated by imposing a single
  constraint on the conventional gravity-based accessibility. Similar to
  the gravity model from which spatial availability is derived, a single
  constraint ensures that the marginals at the destination are met and
  thus the number of opportunities are preserved. Through examples, we
  detail the formulation of the proposed measure. Further, we use data
  from the 2016 Transportation Tomorrow Survey of the Greater Golden
  Horseshoe area in southern Ontario, Canada, to contrast how the
  conventional accessibility measure tends to overestimate and
  underestimate the number of jobs \emph{available} to workers. We
  conclude with some discussion of the possible uses of spatial
  availability and argue that, compared to conventional measures of
  accessibility, it can offer a more meaningful and interpretable
  measure of opportunity access. All data and code used in this research
  are openly available.
  \end{abstract}
  
 \end{frontmatter}

This research was funded by the Mobilizing Justice project.


\end{document}
